Elephant Seal Age JAE Intraspecific Variation

### 2024-05-23 paper/paperv3.qmd
add coef plot for breeding

@@

tibble(
  model = c("Pre-senescence", "Post-senescence"),
  age_coef = c(fixef(breed_age_mod1)["age10"],
               fixef(breed_age_mod2)["age10"]),
  age_coef_se = c(summary(breed_age_mod1)$coef["age10", "Std. Error"],
                  summary(breed_age_mod2)$coef["age10", "Std. Error"]),
  `p(coef<0)` = c(pnorm(summary(breed_age_mod1)$coef["age10", "z value"]),
                  pnorm(summary(breed_age_mod2)$coef["age10", "z value"]))
) %>% 
  mutate(across(where(is.numeric), \(x) signif(x, 3)))

@@

# Age distribution panel A

@@

age_dist | breed_fig

@@

```{r}
#| label: tbl-breed-cap

@@

```{r}
#| label: tbl-breed-success
#| tbl-cap: !expr "tbl_breed_cap"

@@

```{r}
#| label: tbl-survrecruit-cap

@@

```{r}
#| tbl-cap: !expr "surv_recruit_cap"
#| label: tbl-surv_recruit

@@

```{r}
#| label: tbl-pupsex-cap

@@

```{r}
#| label: tbl-pupsex
#| tbl-cap: !expr "pupsex_cap"

@@

```{r}
#| label: tbl-pup-sex
#| tbl-cap: "Offspring sex ratio skewed towards males with increasing maternal age. Mothers age 12, 13, and 17 gave birth to significantly more male than female pups (bold)."

@@

```{r}
#| fig-width: 8

@@

```{r}
ba_data <- phenology_models$model_data[[1]]
ba_mod <- lmer(doy ~ age + (1 | animalID) + (1 | year), data = ba_data)
ba_summary <- summary(ba_mod)
ba_ktable <- ba_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `df`, `t value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|t|)`, digits = 2),
         Response = "Breeding arrival") %>%
  select(-`Pr(>|t|)`) %>% 
  relocate(Response, Parameter)

>>>>

### Raw data

Resighting plot (image) and age structure bar plot

```{r}
#| label: fig-raw-data

age_dist

@@

breed_summ <- tibble(
  model = c("Pre-senescence", "Post-senescence"),
  age_coef = c(fixef(breed_age_mod1)["age10"],
               fixef(breed_age_mod2)["age10"]),
  age_coef_se = c(summary(breed_age_mod1)$coef["age10", "Std. Error"],
                  summary(breed_age_mod2)$coef["age10", "Std. Error"]),
  `p(coef<0)` = c(pnorm(summary(breed_age_mod1)$coef["age10", "z value"]),
                  pnorm(summary(breed_age_mod2)$coef["age10", "z value"]))
)

breed_summ %>% 
  mutate(across(where(is.numeric), \(x) signif(x, 3))) %>%
  set_names(c("Age class", 
              "Age", 
              "se(Age)",
              "p(Age) < 0")) %>% 
  knitr::kable()

@@

@@

# Coefficient panel
breed_coef_fig <- breed_summ %>% 
  mutate(model = fct_rev(model)) %>% 
  ggplot(aes(color = model)) + 
  geom_pointrange(aes(ymin = age_coef - age_coef_se,
                      y = age_coef,
                      ymax = age_coef + age_coef_se,
                      x = model)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual(values = c("cornflowerblue", "firebrick")) +
  labs(y = "Age coefficient") +
  theme_few() +
  theme(legend.position = "none",
        axis.title.x = element_blank())

(breed_fig | breed_coef_fig) + plot_layout(widths = c(3, 1))

@@

```{r, code = FALSE}
#| label: tbl-breed-cap

@@

```{r, code = FALSE}
#| label: tbl-breed-success
tbl-cap: !expr "tbl_breed_cap"

@@

```{r, code = FALSE}
#| label: tbl-survrecruit-cap

@@

```{r, code = FALSE}
#| label: tbl-surv_recruit
tbl-cap: !expr "surv_recruit_cap"

@@

```{r, code = FALSE}
#| label: tbl-pupsex-cap

@@

```{r, code = FALSE}
#| label: tbl-pupsex
tbl-cap: !expr "pupsex_cap"

@@

```{r, code = FALSE}
#| label: tbl-pup-sex
#| tbl-cap: "Offspring sex ratio skewed towards males with increasing maternal age. Mothers age 12, 13, and 17 gave birth to significantly more male than female pups (bold)."

@@

```{r, code = FALSE}
#| fig-width: 8

@@

```{r, code = FALSE}
ba_data <- phenology_models$model_data[[1]]
ba_mod <- lmer(doy ~ age + (1 | animalID) + (1 | year), data = ba_data)
ba_summary <- summary(ba_mod)
ba_ktable <- ba_summary$coefficients %>% 
  as_tibble() %>% 
  mutate(Parameter = c("Intercept", "Age (linear)"),
         across(c(Estimate, `Std. Error`, `df`, `t value`), 
                \(x) format_signif(x, digits = 3)),
         `p value` = format_pval(`Pr(>|t|)`, digits = 2),
         Response = "Breeding arrival") %>%
  select(-`Pr(>|t|)`) %>% 
  relocate(Response, Parameter)
